---
title: "Zillow Project"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
  # pdf_document: 
  #   latex_engine: xelatex
  
---

# Goal of the EDA

Zillow

# Prerequisites for analysis

Following needs to be prior to any analysis:

+ Clear your environment
+ Load required packages
+ Organize work and point to the right directories



```{r, include= FALSE}

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)



```

```{r, include= FALSE }
# Load libraries
#library(here) not used yet
library(tidyverse)
library(corrplot)
library(GGally)
library(gridExtra)
library(readxl)
library(kableExtra)
library(janitor)
library(GGally)
library(psych)
library(stringr)
library(dplyr)
library(openxlsx)
library(knitr)
library(skimr)

```


Load datasets provided with this project.


```{r, warning=FALSE, message=FALSE}
agent_acq_dates <- read.csv("../data/AgentAcquisitionDates.csv")
agentid_zuid <- read.csv("../data/AgentIDZUIDLookup.csv")
agent_leads <- read.csv("../data/AgentLeads.csv")
phone_16_1702 <- read.csv("../data/PhoneCalls20161001_20170228.csv")
phone_1703_1706 <- read.csv("../data/PhoneCalls20170301_20170630.csv")
sales_meet <- read.csv("../data/SalesMeetings.csv")


# agent_acq_dates <- read.csv("AgentAcquisitionDates.csv", header=TRUE)
# agentid_zuid <- read.csv("AgentIDZUIDLookup.csv", header=TRUE)
# agent_leads <- read.csv("agent_leads.csv", header=TRUE)
# phone_16_1702 <- read.csv("PhoneCalls20161001_20170228.csv", header=TRUE)
# phone_1703_1706 <- read.csv("PhoneCalls20170301_20170630.csv", header=TRUE)
# sales_meet <- read.csv("SalesMeetings.csv", header=TRUE)


```


```{r}
# joining agentid_zuid table and agent_acq_dates table  
agentid_acq_dates <- left_join(x = agentid_zuid, y = agent_acq_dates, by = "ZUID") 
# Adding two phone tables together 
phone <- rbind(phone_16_1702, phone_1703_1706) %>% 
  filter(TalkTimeMinutes >= 0.5 ,REAgentID !='', SalesRepID !=''  )

```



```{r}
summary(agent_leads)
summary(phone)
summary(agentid_acq_dates)
summary(sales_meet)
```

+ Most data is from 2016-10-01 to 2017-06-30
+ Agent_Leads file has total of 271k rows 
    + can combine blank rows and unknown rows from LeadType and LeadVendor into one category or remove all
+ agentid_acq_dates records all acquisition, needs to be filtered 
  + missing values can be removed

Things to do:
+ Data type
  + convert datetime columns from all tables into date data type 
+ Data filtering  
  + select date between 2016-10-01 and 2017-06-30 from all tables
+ missing values 



```{r}
# Converting columns DateTime into date data type 
#install.packages("anytime")
library(anytime)
agentid_acq_dates$AcquisitionDate <- anydate(agentid_acq_dates$AcquisitionDate)
agent_leads$LeadDateTime <- anydate(agent_leads$LeadDateTime)
phone$PhoneCallDateTime <- anydate(phone$PhoneCallDateTime)
sales_meet$SalesMeetingDate <- anydate(sales_meet$SalesMeetingDate)
```



Agentid_acq_dates

```{r}
# agentid_acq_dates table 
# select AcquisitionDate between 2016-10-01 and 2017-06-29 from agentid_acq_dates table
agentid_acq_dates <- agentid_acq_dates[(agentid_acq_dates$AcquisitionDate >= "2016-10-01" & agentid_acq_dates$AcquisitionDate <= "2017-06-30"),]

# removing all missing values 
agentid_acq_dates <- agentid_acq_dates %>% drop_na()

summary(agentid_acq_dates)
```





Agent_leads

```{r}
# agent leads table 
# combine social organic and organic as organic
agent_leads$LeadType <- ifelse(agent_leads$LeadType == "", "", 
                               ifelse(agent_leads$LeadType == "unknown", "unknown",
                                      ifelse(agent_leads$LeadType == "Email", "Email",
                                             ifelse(agent_leads$LeadType == "Paid", "Paid",
                                                ifelse(agent_leads$LeadType == "Organic", "Organic",
                                                    ifelse(agent_leads$LeadType == "Social Organic", "Organic", "unknown"))))))

agent_leads$LeadType <- agent_leads$LeadType %>% as.factor()


levels(agent_leads$LeadType)



#regroup leadvendors into paidsocial, paidsearch-bing, paidsearch-google, email, organic and others 


ledvendoremail <- c( "email","gmail","outlook")
ledvendorgoogle <- c("google", "gdn", "android")
ledvendorbing <- c("bing", "msn")
ledvendororganic <- c("bizdev","zillow","organic","trulia","source","internal")
ledvendorsocial <- c("affiliate","facebook","linkedin","display","schools","yahoo","gemini","zrm","areavibes","tomferry","thalamus","irontraffic","twitter","banner","instagram","flagged","brandnetworks","inquiry","textlink","blog","postletsre","tor", "agent","marketing","trulia" ,"draft","listing")


agent_leads$LeadVendor <- ifelse(str_detect(tolower(agent_leads$LeadVendor), ledvendoremail), "Email",
                                ifelse(str_detect(tolower(agent_leads$LeadVendor), ledvendorgoogle), "Paid Search-Google",
                                       ifelse(str_detect(tolower(agent_leads$LeadVendor), ledvendorbing),"Paid Search-Bing",
                                              ifelse(str_detect(tolower(agent_leads$LeadVendor), ledvendororganic),"Organic",
                                                     ifelse(str_detect(tolower(agent_leads$LeadVendor), ledvendorsocial),"PaidSocial","unknown")))))

agent_leads$LeadVendor <- agent_leads$LeadVendor %>% as.factor()

levels(agent_leads$LeadVendor)


agent_leads <- agent_leads   %>% mutate(Channel = ifelse(LeadType =="Email" | LeadVendor =='Email', "Email",
                                                      ifelse(LeadType =="Organic"  | LeadVendor =='Organic', "Organic",
                                                             ifelse(LeadType == "Paid", ifelse(LeadVendor =="Paid Search-Google", "Paid Search-Google",
                                                                                              ifelse(LeadVendor =="Paid Search-Bing", "Paid Search-Bing", "Paid Social")),
                                                                    ifelse(LeadType == "unknown" , "unknown", paste(LeadType,LeadVendor,sep = "-"))))))


agent_leads$Channel <- agent_leads$Channel %>% as.factor()


levels(agent_leads$Channel)

summary(agent_leads)




```





```{r}
# create last touch lead df 
LeadLastTouch <- agent_leads[is.na(agent_leads$LeadVendor) == FALSE,] %>%
                  arrange(REAgentID, desc(LeadDateTime)) %>%       
                  group_by(REAgentID) %>% 
                  mutate(ranking = row_number()) %>%
                  filter(ranking ==1)
# create first touch lead df 
LeadFirstTouch <- agent_leads  %>%    filter(!is.na(LeadDateTime)) %>%
                  arrange(REAgentID, LeadDateTime) %>%      
                  group_by(REAgentID) %>% 
                  mutate(ranking = row_number()) %>%
                  filter(ranking ==1)
# Number of obs each each df are the same    

```



```{r}

#check na value
sapply(agentid_acq_dates, function(x) sum(is.na(x)))
sapply(agent_leads, function(x) sum(is.na(x)))
sapply(phone, function(x) sum(is.na(x)))
sapply(sales_meet, function(x) sum(is.na(x)))



```



```{r}

# calc number touch per lead , last touch attribution
LeadLastTouch %>%   filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
        group_by(Channel) %>%
        summarise(count =n())
# calc number touch per lead , first touch attribution
LeadFirstTouch %>%   filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
        group_by(Channel) %>%
        summarise(count =n())
# the code below use to validate the result about
agent_leads %>% select(REAgentID, SalesRepID, Channel, LeadDateTime) %>% 
                filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
                 group_by(Channel) %>%
                  summarise(Leadcount =n())



```



```{r}
# Join Phone to LEad data and agreegate
dfphonelead <- LeadLastTouch %>% left_join(phone, by =c('REAgentID')) %>%
                                filter(!is.na(LeadDateTime), !is.na(PhoneCallDateTime))%>%
                                select(REAgentID, LeadPlatform, Channel, PhoneCallDateTime) %>% distinct() 
    
dfphonelead %>%   group_by(Channel) %>%
                  summarise(Phonecount =n())
# LeadLastTouch %>% right_join(phonecall, by =c('REAgentID')) %>%
#                                 filter(!is.na(LeadDateTime), !is.na(PhoneCallDateTime))%>%
#                                 select(REAgentID, LeadPlatform, Channel, PhoneCallDateTime) %>% distinct()



```


## Join meeting to phone lead
```{r}
# Salemeeting will be te base, each meeting must be assign to only one lead
dfmeeting <- LeadLastTouch %>% right_join(sales_meet, by=c('REAgentID'))  %>%
                                filter(!is.na(SalesMeetingDate), !is.na(LeadDateTime))%>%
                                select(REAgentID, LeadPlatform, Channel, SalesMeetingDate) %>% distinct() 
dfmeeting %>%   group_by(LeadPlatform,Channel) %>%
                  summarise(Meetingcount =n())
# the different in nuber of meeeting between original data and this dataframe is number of meeting which are not belong to any lead channel
# This mean their lead data is null.
```



## Join accquicistion to Lead

```{r}
# This step I used right join because each acquisition must be link to at least a lead => Acquisition table is the base
dfacquisitionlead <- LeadLastTouch %>% right_join(agentid_acq_dates, by ='REAgentID') %>%
                                      select(REAgentID, LeadPlatform, Channel, AcquisitionDate) %>% distinct()
dfacquisitionlead %>%   group_by(Channel) %>%
                  summarise(Acquiredcount =n())
```



## put all of aggregate data together
```{r}
numlead <- agent_leads %>% select(REAgentID, SalesRepID, Channel, LeadDateTime) %>% 
                filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
                 group_by(Channel) %>%
                  summarise(Leadcount =n())
numphone <- dfphonelead %>%   group_by(Channel) %>%
                  summarise(Phonecount =n())
nummeeting <- dfmeeting %>%   group_by(Channel) %>%
                  summarise(Meetingcount =n())
numacquire <- dfacquisitionlead %>%   group_by(Channel) %>%
                  summarise(Acquiredcount =n())
#final dataframe use for calculate ROI, Conversion rate
#final dataframe use for calculate ROI, Conversion rate
finaldf <- numlead %>% merge(numphone, by.x='Channel', all = TRUE) %>%
                        merge(nummeeting, by.x='Channel', all = TRUE) %>%
                        merge(numacquire, by.x='Channel', all = TRUE)
NoAgenlead <- agent_leads$REAgentID %>% unique() %>% length()
NoAgentAcq <- agent_acq_dates$ZUID %>% unique() %>% length()
# write.csv(finaldf, file = "FinalData.csv")
```


### this part is for modeling

```{r}
basedf <- agent_leads %>% inner_join(phone, by = 'REAgentID') %>%
                        left_join(sales_meet, by =c('REAgentID')) %>%
                        left_join(agentid_acq_dates, by = 'REAgentID')
basedf<- basedf %>% select(REAgentID,LeadPlatform, LeadType, Channel, PhoneCallType,TalkTimeMinutes, SalesMeetingDate, ZUID, AcquisitionDate) %>% distinct() %>%
            mutate(Channel = ifelse(Channel =='-', '', Channel),
                   Meeting = as.factor(ifelse(is.na(SalesMeetingDate),0,1)),
                   ZUID = as.factor(ifelse(is.na(ZUID),0,1) ),
                   Acquired = as.factor(ifelse(is.na(AcquisitionDate),0,1)),
                   PhoneCallType =as.factor(ifelse(PhoneCallType=="Sales Rep Called RE Agent","Out","In")))%>%
            select(LeadPlatform, LeadType,Channel,PhoneCallType ,TalkTimeMinutes,Meeting,Acquired)
          

#logit model
mylogit <- glm(Acquired ~., data = basedf, family = "binomial")
summary(mylogit)
```



Assumptions:
+ Valid phone records are more than 0.5 min and empty records are removed 
+ The revenue is only counted within the period of 2016-10-03 and 2017-06-30

AgentLeads Table 
LeadType
+ origanic and social organic are the same group 
+ left blank and unknown value as they are

LeadVendor
+ Regrouped leadvendor into five categories based on our assumption on each category


Last touch
+ we associate the total acquisitions by last touch attribution 

Join tables by only REAgentID
+ To keep number of Agent ID consistent and not being excluded by join table
+ this will cause many duplicate, but we can remve these duplicate later after join
















