---
title: "Zillow Project"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
  # pdf_document: 
  #   latex_engine: xelatex
  
---

# Goal of the EDA

Zillow

# Prerequisites for analysis

Following needs to be prior to any analysis:

+ Clear your environment
+ Load required packages
+ Organize work and point to the right directories



```{r, include= FALSE}

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)



```

```{r, include= FALSE }
# Load libraries
#library(here) not used yet
library(tidyverse)
library(corrplot)
library(GGally)
library(gridExtra)
library(readxl)
library(kableExtra)
library(janitor)
library(GGally)
library(psych)
library(stringr)
library(dplyr)
library(openxlsx)
library(knitr)
library(skimr)

```


Load datasets provided with this project.


```{r, warning=FALSE, message=FALSE}
agent_acq_dates <- read.csv("../data/AgentAcquisitionDates.csv")
agentid_zuid <- read.csv("../data/AgentIDZUIDLookup.csv")
agent_leads <- read.csv("../data/AgentLeads.csv")
phone_16_1702 <- read.csv("../data/PhoneCalls20161001_20170228.csv")
phone_1703_1706 <- read.csv("../data/PhoneCalls20170301_20170630.csv")
sales_meet <- read.csv("../data/SalesMeetings.csv")


# agent_acq_dates <- read.csv("AgentAcquisitionDates.csv", header=TRUE)
# agentid_zuid <- read.csv("AgentIDZUIDLookup.csv", header=TRUE)
# agent_leads <- read.csv("AgentLeads.csv", header=TRUE)
# phone_16_1702 <- read.csv("PhoneCalls20161001_20170228.csv", header=TRUE)
# phone_1703_1706 <- read.csv("PhoneCalls20170301_20170630.csv", header=TRUE)
# sales_meet <- read.csv("SalesMeetings.csv", header=TRUE)


```


```{r}
# joining agentid_zuid table and agent_acq_dates table  
agentid_acq_dates <- merge(x = agentid_zuid, y = agent_acq_dates, by.x = "ZUID", by.y = "ZUID", all= TRUE) 
# Adding two phone tables together 
phone <- rbind(phone_16_1702, phone_1703_1706)
```



```{r}
summary(agent_leads)
summary(phone)
summary(agentid_acq_dates)
summary(sales_meet)
```

+ Most data is from 2016-10-01 to 2017-06-30
+ Agent_Leads file has total of 271k rows 
    + can combine blank rows and unknown rows from LeadType and LeadVendor into one category or remove all
+ agentid_acq_dates records all acquisition, needs to be filtered 
  + missing values can be removed

Things to do:
+ Data type
  + convert datetime columns from all tables into date data type 
+ Data filtering  
  + select date between 2016-10-01 and 2017-06-30 from all tables
+ missing values 



```{r}
# Converting columns DateTime into date data type 
library(anytime)
agentid_acq_dates$AcquisitionDate <- anydate(agentid_acq_dates$AcquisitionDate)
agent_leads$LeadDateTime <- anydate(agent_leads$LeadDateTime)
phone$PhoneCallDateTime <- anydate(phone$PhoneCallDateTime)
sales_meet$SalesMeetingDate <- anydate(sales_meet$SalesMeetingDate)
```



Agentid_acq_dates

```{r}
# agentid_acq_dates table 
# select AcquisitionDate between 2016-10-01 and 2017-06-29 from agentid_acq_dates table
agentid_acq_dates <- agentid_acq_dates[(agentid_acq_dates$AcquisitionDate >= "2016-10-01" & agentid_acq_dates$AcquisitionDate <= "2017-06-29"),]

# removing all missing values 
agentid_acq_dates <- agentid_acq_dates %>% drop_na()

summary(agentid_acq_dates)
```


Agent_leads

```{r}
# agent leads table 
# combine social organic and organic as organic, unknown and blank as unknown
agent_leads$LeadType <- ifelse(agent_leads$LeadType == "", "unknown", 
                               ifelse(agent_leads$LeadType == "unknown", "unknown",
                                      ifelse(agent_leads$LeadType == "Email", "Email",
                                             ifelse(agent_leads$LeadType == "Paid", "Paid",
                                                ifelse(agent_leads$LeadType == "Organic", "Organic",
                                                    ifelse(agent_leads$LeadType == "Social Organic", "Organic", "unknown"))))))

agent_leads$LeadType <- agent_leads$LeadType %>% as.factor()


# remove and blank values from Leadtype 
agent_leads <- agent_leads[!agent_leads$LeadType == "unknown",]

summary(agent_leads)

```

+ LeadVendor has too many levels, and is a description of LeadType. We can either ignore the variable or do futher grouping if we have time


Phone

```{r}
# Removing TalkTimeMInutes values that equal to 0 
summary(phone)

phone <- phone[!phone$TalkTimeMinutes == 0 & phone$TalkTimeMinutes <= 1000,]
```

Sales_meet
```{r}
summary(sales_meet)
```





Questions:

+ Should we filter out records prior to 2017-03-13 since sales_meeting only has records after the period?
+ Need to filter TalkTimeMinutes from phone table  
+ Take a look at missing values. I simply removed all missings values from agentid_acq_dates, and combined unknown and missing values from agent_leads










