---
title: "R Notebook"
output: html_notebook
---


Commented header  
=========================================

```{r echo = TRUE}
# Course: 
# Title: 
# Purpose: 
# Date: 
# Author: Huy LE
```


Clear environment of variables and packages  
=========================================

```{r}

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```

Load packages that include different functions  
=========================================

```{r}
# adding library
library(tidyverse)
library(GGally)
library(gridExtra)
library("readxl")
library(janitor)
library(stringr)
library(aod)
library(ggplot2)
```

Load data and begin new EDA  
=========================================

```{r}
#loading data
AgentAcquisitionDates <- read_csv('../data/AgentAcquisitionDates.csv')
AgentIDZUIDLookup <- read_csv('../data/AgentIDZUIDLookup.csv')
AgentLeads <- read_csv('../data/AgentLeads.csv')
PhoneCalls20161001_20170228 <- read_csv('../data/PhoneCalls20161001_20170228.csv')
PhoneCalls20170301_20170630 <- read_csv('../data/PhoneCalls20170301_20170630.csv')
SalesMeetings <- read_csv('../data/SalesMeetings.csv')


```

```{r}
# filter all acquisition before OCt 2016

AgentAcquisitionDates$AcquisitionDate <- as.Date(AgentAcquisitionDates$AcquisitionDate,"%Y-%m-%d")
# remove accquisition before OCt 2016
AgentAcquisitionDates <- AgentAcquisitionDates %>% filter(AcquisitionDate >= as.Date("2016-10-1"))


# union phone call data
phonecall <- rbind(PhoneCalls20161001_20170228, PhoneCalls20170301_20170630) %>%
              filter(TalkTimeMinutes >= 0.5 ,REAgentID !='', SalesRepID !=''  )

#Convert NA to  ''. This step is necessary, because NA will cause trouble when aggregate.
AgentLeads$LeadType[is.na(AgentLeads$LeadType) == TRUE] <- ""
AgentLeads$LeadVendor[is.na(AgentLeads$LeadVendor) == TRUE] <- ""

# 
AgentLeads$LeadType %>% unique()
# #   
AgentLeads$LeadPlatform%>% unique()
# # 
AgentLeads$LeadVendor%>% unique()


AgentLeads$LeadType <- ifelse(AgentLeads$LeadType == "", "", 
                                 ifelse(AgentLeads$LeadType == "unknown", "unknown",
                                        ifelse(AgentLeads$LeadType == "Email", "Email",
                                               ifelse(AgentLeads$LeadType == "Paid", "Paid",
                                                  ifelse(AgentLeads$LeadType == "Organic", "Organic",
                                                      ifelse(AgentLeads$LeadType == "Social Organic", "Organic","unknow"))))))

# Group lead vendor to group as marketing channel
# 
ledvendoremail <- c( "email","gmail","outlook")
ledvendorgoogle <- c("google", "gdn", "android")
ledvendorbing <- c("bing", "msn")
ledvendororganic <- c("bizdev","zillow","organic","trulia","source","internal")
ledvendorsocial <- c("affiliate","facebook","linkedin","display","schools","yahoo","gemini","zrm","areavibes","tomferry","thalamus","irontraffic","twitter","banner","instagram","flagged","brandnetworks","inquiry","textlink","blog","postletsre","tor", "agent","marketing","draft","listing")

# by detecting the patern of Leadvender, I assing each vendor to a category
AgentLeads$LeadVendor <- ifelse(str_detect(tolower(AgentLeads$LeadVendor), ledvendoremail), "Email",
                                ifelse(str_detect(tolower(AgentLeads$LeadVendor), ledvendorgoogle), "Google",
                                       ifelse(str_detect(tolower(AgentLeads$LeadVendor), ledvendorbing),"Bing",
                                              ifelse(str_detect(tolower(AgentLeads$LeadVendor), ledvendororganic),"Organic",
                                                     ifelse(str_detect(tolower(AgentLeads$LeadVendor), ledvendorsocial),"Social", "unknow")))))
     
# after group vendor category, I use this rule to set which channle the lead belong to                                                       
AgentLeads <- AgentLeads   %>% mutate(Channel = ifelse(LeadType =="Email" | LeadVendor =='Email', "Email",
                                                      ifelse(LeadType =="Organic"  | LeadVendor =='Organic', "Organic",
                                                             ifelse(LeadType == "Paid", ifelse(LeadVendor =="Google", "Paid Google",
                                                                                              ifelse(LeadVendor =="Bing", "Paid Bing", "Paid Social")),
                                                                    ifelse(LeadType == "unknow" , "unknow", paste(LeadType,LeadVendor,sep = "-"))))))


# create last touch lead df 
LeadLastTouch <- AgentLeads[is.na(AgentLeads$LeadVendor) == FALSE,] %>%
                  arrange(REAgentID, desc(LeadDateTime)) %>%       #< Sort relevant columns
                  group_by(REAgentID) %>% 
                  mutate(ranking = row_number()) %>%
                  filter(ranking ==1)

# create first touch lead df 
LeadFirstTouch <- AgentLeads  %>%    filter(!is.na(LeadDateTime)) %>%
                  arrange(REAgentID, LeadDateTime) %>%       #< Sort relevant columns
                  group_by(REAgentID) %>% 
                  mutate(ranking = row_number()) %>%
                  filter(ranking ==1)
# Number of obs each each df are the same                  

```


```{r}
#check na value
sapply(AgentAcquisitionDates, function(x) sum(is.na(x)))
sapply(AgentIDZUIDLookup, function(x) sum(is.na(x)))
sapply(AgentLeads, function(x) sum(is.na(x)))
sapply(PhoneCalls20161001_20170228, function(x) sum(is.na(x)))
sapply(PhoneCalls20170301_20170630, function(x) sum(is.na(x)))
sapply(SalesMeetings, function(x) sum(is.na(x)))

#check duplicate row
#duplicated(AgentLeads)
agentlead <- AgentLeads%>%distinct() 
phonecall <- phonecall%>% distinct() 

```


### the process is: Lead -> Phone Call -> Meeting or not -> acquicisiton datte


## This Chunk will work only in aggregate total lead in each channel
```{r}
# calc number touch per lead , last touch attribution
LeadLastTouch %>%   filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
        group_by(Channel) %>%
        summarise(count =n())

# calc number touch per lead , first touch attribution
LeadFirstTouch %>%   filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
        group_by(Channel) %>%
        summarise(count =n())

# the code below use to validate the result about
AgentLeads %>% select(REAgentID, SalesRepID, Channel, LeadDateTime) %>% 
                filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
                 group_by(Channel) %>%
                  summarise(Leadcount =n())
``` 


```{r}
# Join Phone to LEad data and agreegate
dfphonelead <- LeadLastTouch %>% left_join(phonecall, by =c('REAgentID')) %>%
                                filter(!is.na(LeadDateTime), !is.na(PhoneCallDateTime))%>%
                                select(REAgentID, LeadPlatform, Channel, PhoneCallDateTime) %>% distinct() 
    
dfphonelead %>%   group_by(Channel) %>%
                  summarise(Phonecount =n())
# LeadLastTouch %>% right_join(phonecall, by =c('REAgentID')) %>%
#                                 filter(!is.na(LeadDateTime), !is.na(PhoneCallDateTime))%>%
#                                 select(REAgentID, LeadPlatform, Channel, PhoneCallDateTime) %>% distinct()

```


## Join meeting to phone lead
```{r}

# Salemeeting will be te base, each meeting must be assign to only one lead
dfmeeting <- LeadLastTouch %>% right_join(SalesMeetings, by=c('REAgentID'))  %>%
                                filter(!is.na(SalesMeetingDate), !is.na(LeadDateTime))%>%
                                select(REAgentID, LeadPlatform, Channel, SalesMeetingDate) %>% distinct() 


dfmeeting %>%   group_by(LeadPlatform,Channel) %>%
                  summarise(Meetingcount =n())
# the different in nuber of meeeting between original data and this dataframe is number of meeting which are not belong to any lead channel
# This mean their lead data is null.

```

## Join accquicistion to Lead

```{r}
# join ZUID acquisition <-> Agent ID
df <- AgentAcquisitionDates %>% right_join(AgentIDZUIDLookup, by = 'ZUID') %>%
                                filter(!is.na(AcquisitionDate))
head(df)


# This step I used right join because each acquisition must be link to at least a lead => Acquisition table is the base
dfacquisitionlead <- LeadLastTouch %>% right_join(df, by ='REAgentID') %>%
                                      select(REAgentID, LeadPlatform, Channel, AcquisitionDate) %>% distinct()


dfacquisitionlead %>%   group_by(Channel) %>%
                  summarise(Acquiredcount =n())
```



## put all of aggregate data together
```{r}
numlead <- AgentLeads %>% select(REAgentID, SalesRepID, Channel, LeadDateTime) %>% 
                filter(REAgentID != '', SalesRepID !='', !is.na(LeadDateTime)) %>% distinct() %>%
                 group_by(Channel) %>%
                  summarise(Leadcount =n())
numphone <- dfphonelead %>%   group_by(Channel) %>%
                  summarise(Phonecount =n())

nummeeting <- dfmeeting %>%   group_by(Channel) %>%
                  summarise(Meetingcount =n())
numacquire <- dfacquisitionlead %>%   group_by(Channel) %>%
                  summarise(Acquiredcount =n())


#final dataframe use for calculate ROI, Conversion rate
finaldf <- numlead %>% merge(numphone, by.x='Channel', all = TRUE) %>%
                        merge(nummeeting, by.x='Channel', all = TRUE) %>%
                        merge(numacquire, by.x='Channel', all = TRUE)

##########
# Group "-", "Unknow"

                        
NoAgenlead <- AgentLeads$REAgentID %>% unique() %>% length()
NoAgentAcq <- AgentAcquisitionDates$ZUID %>% unique() %>% length()

write.csv(finaldf, file = "FinalData.csv")

```


# FIrst touch Attribution
```{r}

```



### this part is for modeling

```{r}
basedf <- AgentLeads %>% inner_join(phonecall, by = 'REAgentID') %>%
                        left_join(SalesMeetings, by =c('REAgentID')) %>%
                        left_join(df, by = 'REAgentID')

basedf$Channel %>% unique()
basedf<- basedf %>% select(REAgentID,LeadPlatform, LeadType, Channel, PhoneCallType,TalkTimeMinutes, SalesMeetingDate, ZUID, AcquisitionDate) %>% distinct() %>%
            mutate(Channel = ifelse(Channel =='-', '', 
                                    ifelse(str_detect(tolower(Channel),'unknown'),'unknown', Channel)),
                   Meeting = as.factor(ifelse(is.na(SalesMeetingDate),0,1)),
                   ZUID = as.factor(ifelse(is.na(ZUID),0,1) ),
                   Acquired = as.factor(ifelse(is.na(AcquisitionDate),0,1)),
                   PhoneCallType =as.factor(ifelse(PhoneCallType=="Sales Rep Called RE Agent","Out","In")))%>%
            select(LeadPlatform, LeadType,Channel,PhoneCallType ,TalkTimeMinutes,Meeting,Acquired)
          

#logit model

mylogit <- glm(Acquired ~., data = basedf, family = "binomial")

summary(mylogit)

logitresult <- as.data.frame(summary(mylogit)$coefficients)[,c("Estimate","Std. Error", "Pr(>|z|)")]

logitresult$oddratio <- exp(coef(mylogit))[1:14]
logitresult
```



